---
title: "R Notebook"
output: html_notebook
---

Translating Sara's STATA codes: 


```{r}
rm(list=ls())

library(tidyverse)
library(sjmisc)

fresco.1<- read.csv(file.choose(), header = T)#datafeeddetail
fresco.2<- read.csv(file.choose(), header=T)#datafeedheader
```

********************************************************************************
*** MERGE AND CLEAN DATA ***
*******************************************************************************
* INSTRUCTIONS:

* Download new header and detail .CSV files from SFTP site- it should have arrived on or around the 5th of the month. 
* Save both CSV files in your "working directory" for Stata (a folder on your computer designated for Mas Fresco data and outputs). 
* Rename the MAY header file as UCSDMonthlyDataFeedHeader_2021_05.csv and the detail file as  UCSDMonthlyDataFeedDetails_2021_05.csv <--- must be exactly like this

######
set more off

*Merging raw Header and Details Data Files from Northgate

*Create raw Header dataset
cd "/Users/sarahhillervenegas/Dropbox/2 MAS FRESCO 2/1 Mas Fresco Data-Analysis-IRB KR SHV/2 Raw Northgate POS Data"
insheet using "UCSD Data Feed Header Feb to Aug 2017.csv"
cd "/Users/sarahhillervenegas/Dropbox/2 MAS FRESCO 2/1 Mas Fresco Data-Analysis-IRB KR SHV/3 MF STATA"
save UCSDDataFeedHeaderFebtoAug2017, replace
clear  

```{r merging raw header and details data}
#cd in stata means change working directories
#insheet using "*.csv" --> read.csv (done)
#for this project, we only have files reflecting 02.2021
```

Use by(storeid posid transactionid transactiondate loyaltycard) to collapse and merge from now on. 
*The following "mega ID" will allow you to isolate individual transactions and merge with detail data
*gen mega_id= storeid*posid*transactionid*transactiondate*loyaltycard
*sort mega_id
*format mega_id %30.0f

format loyaltycard %11.0f

```{r creating a new ID variable}

fresco.2<-fresco.2%>%
  unite("mega_id", c(Storeid, Transaction.ID, 
                     Transaction.Date, LoyaltyCard), 
        na.rm = F, remove = F)


```

*New date code that required re-doing all previous .csv insheeting 
gen stata_transactiondate = date(transactiondate, "MD20Y")
format stata_transactiondate %tdn/d/Y

```{r formatting date}
fresco.2<- fresco.2%>%
  mutate(stata_transactiondate=lubridate::mdy(Transaction.Date))

```

*CREATING SEPARATE GROUPS FOR YEAR 1, YEAR 2, and YEAR 3- CHANGE TO UPDATE FOR NEW GROUP RANGES
gen group=.
replace group=1 if loyaltycard >=48700189000 & loyaltycard<=48700277153
replace group=2 if loyaltycard >=48700277174 & loyaltycard<=48700278406
replace group=3 if loyaltycard >=48700278407 & loyaltycard<=48700279927
replace group=4 if loyaltycard >=48700279953 & loyaltycard<=48700280999
replace group=5 if loyaltycard >=41100304213 & loyaltycard<=41100306000
replace group=4 if loyaltycard ==41100304090
replace group=5 if loyaltycard ==48700279955
replace group=5 if loyaltycard ==48700279956
replace group=5 if loyaltycard ==48700279957
replace group=5 if loyaltycard ==48700279959

```{r}
fresco.2<- fresco.2%>%
  mutate(group = sjmisc::rec(fresco.2$LoyaltyCard, rec = "48700189000:48700277153=1;
                     48700277174:48700278406=2; 48700278407:48700279927=3;
                     48700279953:48700280999=4; 41100304213: 41100306000=5"))%>%
  sjmisc::rec(fresco.2$group, rec="41100304090,48700279955:48700279957,48700279959=5")
```
